A secondary screen architecture to accurately capture viewers' interactions in an iTV environment

### 2014-05-19 src/paper.tex
Removed some parts of the introduction

The interactions between viewers and TV can be classified as implicit and explicit. Implicit interactions are part of the natural actions of watching TV (e.g., changing channels). In explicit interactions, viewers contribute by actively evaluating, commenting, or sharing their opinion about a given content. Both kinds of interaction are important for applications that rely on audience generated data.

Considering the interactions of millions of viewers, the captured data can provide valuable information for content providers (CPs)~\cite{Teixeira2010}. For example, the CPs can obtain the user ratings given to TV programs, amount of viewers, and user profiles. By using proper machine learning algorithms, CPs can infer viewers' tastes from audience data in order to deliver personalized content~\cite{Kim2012,Shin2009}. However, identifying viewers and capturing their individual interactions are still a challenging activity in the traditional TV environment, which consists of the TV and viewers interacting through a remote control (RC).

>>>>

% The interactions between viewers and TV can be classified as implicit and explicit. Implicit interactions are part of the natural actions of watching TV (e.g., changing channels). In explicit interactions, viewers contribute by actively evaluating, commenting, or sharing their opinion about a given content. Both kinds of interaction are important for applications that rely on audience generated data.

Considering the interactions of millions of viewers, the captured data can provide valuable information for content providers (CPs)~\cite{Teixeira2010}. For example, the CPs can obtain the user ratings given to TV programs, amount of viewers, and user profiles. By using proper machine learning algorithms, CPs can infer viewers' tastes from audience data in order to deliver personalized content~\cite{Kim2012,Shin2009}. However, identifying viewers and capturing their individual interactions are still a challenging activity in the traditional TV environment.%, which consists of the TV and viewers interacting through a remote control (RC).
